Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-31 doc/journal/fpgapaperfinal/FPGAPaper/partitioning.tex
resolved some todos
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4573 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

Figure \ref{fig:hyperedge_to_graph} shows how a netlist of three blocks and two nets is transformed into its component subgraphs. TODO JAVEED: Maybe just show star 1/n from start to finish.

@@

To select the best hyperedge model, we used the Metis partitioner to generate graph partitions (which assign each vertex to a partition number) and applied the partitioning result to the original untransformed hypergraph. To rank the different models, we computed the \emph{hyperedge cutsize} for every hyperedge model, across several circuits. The hyperedge cutsize is the number of hyperedges crossing the cutline, as illustrated in Figure \ref{fig:hyperedge_cutline}. As it equals the number of nets that cross the interposer boundary, it is a measure of circuit routability. The results are shown in Figure \ref{fig:graph_topology_cutsize}.

@@

\begin{figure}[!htbp]
\centering
\input{graph_topology_mcw}
%\includegraphics[width=\linewidth]{graph_topology_mcw.eps}
\caption{Minimum channel width achieved by VPR with different hyperedge models and weightings. n is the number of vertices on a hyperedge. TODO JAVEED: Which circuits?}
\label{fig:graph_topology_mcw}
\end{figure}

>>>>

Figure \ref{fig:hyperedge_to_graph} shows how a netlist of three blocks and two nets is transformed into its component subgraphs.

@@

To select the best hyperedge model, we used the Metis partitioner to generate graph partitions (which assign each vertex to a partition number) and applied the partitioning result to the original untransformed hypergraph. To rank the different models, we computed the \emph{hyperedge cutsize} for every hyperedge model, across the same circuits as in Section \ref{sec:CADeffect}. The hyperedge cutsize is the number of hyperedges crossing the cutline, as illustrated in Figure \ref{fig:hyperedge_cutline}. As it equals the number of nets that cross the interposer boundary, it is a measure of circuit routability. The results are shown in Figure \ref{fig:graph_topology_cutsize}.

@@

\begin{figure}[!htbp]
\centering
\input{graph_topology_mcw}
%\includegraphics[width=\linewidth]{graph_topology_mcw.eps}
\caption{Minimum channel width achieved by VPR with different hyperedge models and weightings. n is the number of vertices on a hyperedge.}
\label{fig:graph_topology_mcw}
\end{figure}
